FictionEro - Affective Impact of Fiction

### 2025-10-09 analysis/analysis.qmd
Update analysis.qmd

```{r Arousal1}
#| fig-width: 12
arousal_dist1 <- df1 |>
  ggplot(aes(x=Arousal, fill = Condition)) +
  geom_histogram(position = "identity", alpha = 0.4, colour = "black", bins = 20) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Arousal Study 1", ) +
  facet_wrap(~Gender) +
   scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

@@

@@

```{r}
results_table(arousal1)
```

```{r}
results_table(arousal2)

@@

  plt <- pred_df |>
    ggplot(aes(x = ConditionBelief, y = Proportion,color = Condition, linetype = Sample, group = interaction(Sample, Condition)
    )) +
    geom_hline(yintercept = 0, color = "darkgrey") +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.1) +
    facet_grid(Relevance ~ Gender, switch = "y") +
    scale_color_manual(values = c("AI-Generated" = "#2196F3","Photograph" = "#F44336")) +
    theme_minimal(base_size = 14) +
    labs(title = title, x= "Whether the original labels were believed to be true",color = "Images presented as:", linetype = "Sample"
    ) +
    theme(
      axis.title.y = element_blank(),
      axis.text.y = element_text(size = 8),
      strip.placement = "outside",
      strip.background.x = element_rect(fill = "lightgrey", color = NA),
      strip.text.x = element_text(size = 10),
      strip.text.y = element_text(size = 10),
      axis.text.x = element_text(face = "bold", size = 9, color = "black"),
      legend.text = element_text(size = 10),
      legend.position = "bottom")

@@

```{r}
results_table(enticement1)
```

```{r}
results_table(enticement2)
```

@@

```{r}
results_table(valence1)
```

```{r}
results_table(valence2)
```

@@

```{r}

model_draft <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition|Participant) + (1|Item),
                          data=df2,
                          family=glmmTMB::ordbeta(),
                          control = glmmTMB::glmmTMBControl(parallel = 8))

```
### Reliability

>>>>

```{r Arousal1}
#| fig-width: 12
arousal_dist1 <- df1 |>
  ggplot(aes(x=Arousal, fill = Condition)) +
  geom_histogram(position = "identity", alpha = 0.5, colour = "black", bins = 30) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Arousal Study 1", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

```{r Arousal1}
#| fig-width: 12
arousal_dist1 <- df1 |>
  ggplot(aes(x=Arousal, fill = Condition)) +
  geom_histogram(position = "identity", alpha = 0.5, colour = "black", bins = 30) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Arousal Study 1", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

### Enticment Distributions

```{r Arousal1}
#| fig-width: 12
enticement_dist1 <- df1 |>
  ggplot(aes(x=Enticement, fill = Condition)) +
  geom_histogram(position = "identity", alpha = 0.5, colour = "black", bins = 30) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Enticement Study 1", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

enticement_dist1
```

```{r Arousal2}
#| fig-width: 12
enticement_dist2 <- df2 |>
  ggplot(aes(x=Enticing, fill = Condition)) +
  geom_bar(position = "identity", alpha = 0.5, line = "black") +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Enticment Study 2", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

enticement_dist2
```

### Valence Distributions

```{r Arousal1}
#| fig-width: 12
valence_dist1 <- df1 |>
  ggplot(aes(x=Valence, fill = Condition)) +
  geom_histogram(position = "identity", alpha = 0.5, colour = "black", bins = 30) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Valence Study 1", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

valence_dist1
```

```{r Arousal2}
#| fig-width: 12
valence_dist2 <- df2 |>
  ggplot(aes(x=Valence, fill = Condition)) +
  geom_bar(position = "identity", alpha = 0.5, line = "black") +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Valence Study 2", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

valence_dist2
```

@@

```{r}
params_table <- function(m) {
  d <- as.data.frame(m, variable = insight::find_parameters(m, effects = "fixed", flatten  = TRUE))
  t <- bayestestR::describe_posterior(d, effects = "fixed", component = "all", ci_method = "hdi", test = "p_direction")
  out <- insight::format_table(t)
  out |> 
    mutate(col = t$pd) |> 
    gt::gt() |> 
    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
                   row = col > 0.95, palette = "yellow") |> 
    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
                   row = col > 0.97, palette = "green") |> 
    gt::cols_hide("col")
 }
```

@@

```{r}
params_table(arousal1)
summary(arousal1, robust = TRUE)
```

```{r}
params_table(arousal2)
summary(arousal2, robust = TRUE)

@@

  plt <- pred_df |>
    ggplot(aes(x = ConditionBelief, y = Estimate,color = Condition, linetype = Sample, group = interaction(Sample, Condition)
    )) +
    geom_hline(yintercept = 0, color = "darkgrey") +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.1) +
    facet_grid(Relevance ~ Gender, switch = "y") +
    scale_color_manual(values = c("AI-Generated" = "#2196F3","Photograph" = "#F44336")) +
    theme_minimal(base_size = 14) +
    labs(title = title, x= "Whether the original labels were believed to be true",color = "Images presented as:", linetype = "Sample"
    ) +
    theme(
      axis.title.y = element_blank(),
      axis.text.y = element_text(size = 8),
      strip.placement = "outside",
      strip.background.x = element_rect(fill = "lightgrey", color = NA),
      strip.text.x = element_text(size = 10),
      strip.text.y = element_text(size = 10),
      axis.text.x = element_text(face = "bold", size = 9, color = "black"),
      legend.text = element_text(size = 10),
      legend.position = "bottom")

@@

```{r}
params_table(enticement1)
summary(enticement1, robust = TRUE)
```

```{r}
params_table(enticement2)
summary(enticement2, robust = TRUE)

@@

```{r}
params_table(valence1)
summary(valence1, robust = TRUE)
```

```{r}
params_table(valence2)
summary(valence2, robust = TRUE)

@@

### Reliability
